# CUNY    SPS    R-WORKSHOP
## Final Assignment
### Tage N Singh
#### This Project use A Consolidate Dataset From 1969 to 1989 and is accessed from github.
#### The Question ? ?
#### -- Is THERE CORRELATION ACROSS REGIONS/STATES (AND DC) IN THE US AMONG THE FOLLOWING : :
#### -- US BIRTH RATES
#### -- MEDIAN HOUSEHOLD INCOME
#### -- PER CAPITA HOUSEHOLD INCOME
#### -- US GROSS DEOMESTIC PRODUCT (GDP)
#### -- FOR THE DECADES ENDING 1969, 1979,1989
#### -- ( CURRENT DOLLARS)


### - (:

```{r,Introduction}
library(datasets)
library(ggplot2)
library(dplyr)
library("tidyverse")




popstatsURL <- ("https://raw.githubusercontent.com/tagensingh/SPS-WRKSHP-R-FINAL-PROJECT/master/1-SPS-Project-Consolidate-Data.csv")
popstatsURL <- ("1-SPS-Project-Consolidate-Data.csv")
popstats1 <- read.table(file =popstatsURL, header = TRUE , sep = ",")

summary(popstats1)

```

#### -- Fixing The Headers

```{r, Headers}

popstats2 <- popstats1

names(popstats2)[1] <- "Region_Code"
names(popstats2)[2] <- "Region_Name"
names(popstats2)[3] <- "State_Code"
names(popstats2)[4] <- "State_Name"
names(popstats2)[5] <- "Births_1969"
names(popstats2)[6] <- "Births_1979"
names(popstats2)[7] <- "Births_1989"
names(popstats2)[8] <- "GDP_1969"
names(popstats2)[9] <- "GDP_1979"
names(popstats2)[10] <- "GDP_1989"
names(popstats2)[11] <- "Median_HH_Inc_1969"
names(popstats2)[12] <- "Median_HH_Inc_1979"
names(popstats2)[13] <- "Median_HH_Inc_19689"
names(popstats2)[14] <- "Per_Capita_HH_Inc_1969"
names(popstats2)[15] <- "Per_Capita_HH_Inc_1979"
names(popstats2)[16] <- "Per_Capita_HH_Inc_1989"


head(popstats2, 6)

```

####Computing the correlation By State

```{r,Computation_1}
popstats31 <- subset(popstats2, Region_Code == "1",select=Region_Name:Per_Capita_HH_Inc_1989)
popstats32 <- subset(popstats2, Region_Code == "2",select=Region_Name:Per_Capita_HH_Inc_1989)
popstats33 <- subset(popstats2, Region_Code == "3",select=Region_Name:Per_Capita_HH_Inc_1989)
popstats34 <- subset(popstats2, Region_Code == "4",select=Region_Name:Per_Capita_HH_Inc_1989)
popstats35 <- subset(popstats2, Region_Code == "5",select=Region_Name:Per_Capita_HH_Inc_1989)
popstats36 <- subset(popstats2, Region_Code == "6",select=Region_Name:Per_Capita_HH_Inc_1989)
popstats37 <- subset(popstats2, Region_Code == "7",select=Region_Name:Per_Capita_HH_Inc_1989)
popstats38 <- subset(popstats2, Region_Code == "8",select=Region_Name:Per_Capita_HH_Inc_1989)
popstats39 <- subset(popstats2, Region_Code == "9",select=Region_Name:Per_Capita_HH_Inc_1989)
popstats40 <- subset(popstats2, Region_Code == "10",select=Region_Name:Per_Capita_HH_Inc_1989)
popstats41 <- subset(popstats2, Region_Code == "11",select=Region_Name:Per_Capita_HH_Inc_1989)



head(popstats31, 6)
head(popstats32, 6)
head(popstats33, 6)
head(popstats34, 6)
head(popstats35, 6)
head(popstats36, 6)
head(popstats37, 6)
head(popstats38, 6)
head(popstats39, 6)
head(popstats40, 6)
head(popstats41, 6)



```

#### Plotting the graphs

```{r,graphsprep}
library("ggpubr")


regionsURL <- ("https://raw.githubusercontent.com/tagensingh/SPS-WRKSHP-R-FINAL-PROJECT/master/Regions_Totals.csv")
regionsURL <- ("Regions_Totals.csv")
regions <- read.table(file =regionsURL, header = TRUE , sep = ",")

summary(regions)


names(regions)[1] <- "Region"
names(regions)[2] <- "Births_1969"
names(regions)[3] <- "Births_1979"
names(regions)[4] <- "Births_1989"
names(regions)[5] <- "GDP_1969"
names(regions)[6] <- "GDP_1979"
names(regions)[7] <- "GDP_1989"
names(regions)[8] <- "Median_HH_Inc_1969"
names(regions)[9] <- "Median_HH_Inc_1979"
names(regions)[10] <- "Median_HH_Inc_1989"
names(regions)[11] <- "Per_Capita_HH_Inc_1969"
names(regions)[12] <- "Per_Capita_HH_Inc_1979"
names(regions)[13] <- "Per_Capita_HH_Inc_1989"

print("The Summary Table by Region is as follows")

summary(regions)

head(regions,12)

```


```{r,Graphs1969}

ggscatter(regions, x = "Births_1969", y = "GDP_1969", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Births 1969", ylab = "GDP 1969")

##

ggscatter(regions, x = "Births_1969", y = "Median_HH_Inc_1969", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Births 1969", ylab = "Median HH Inc 1969")


##

ggscatter(regions, x = "Births_1969", y = "Per_Capita_HH_Inc_1969", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Births 1969", ylab = "Per Capita HH Inc 1969")

```


```{r,Graphs1979}

ggscatter(regions, x = "Births_1979", y = "GDP_1979", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Births 1979", ylab = "GDP 1979")

##

ggscatter(regions, x = "Births_1979", y = "Median_HH_Inc_1979", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Births 1979", ylab = "Median HH Inc 1979")


##

ggscatter(regions, x = "Births_1979", y = "Per_Capita_HH_Inc_1979", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Births 1979", ylab = "Per Capita HH Inc 1979")

```


```{r,Graphs1989}

ggscatter(regions, x = "Births_1989", y = "GDP_1989", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Births 1989", ylab = "GDP 1989")

##

ggscatter(regions, x = "Births_1989", y = "Median_HH_Inc_1989", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Births 1989", ylab = "Median HH Inc 1989")


##

ggscatter(regions, x = "Births_1989", y = "Per_Capita_HH_Inc_1989", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Births 1989", ylab = "Per Capita HH Inc 1989")

```


```{r,correlation_calcs}

## - Births 1969 to GDP 1969
b1969_g1969 <- cor.test(regions$Births_1969, regions$GDP_1969, 
                    method = "pearson")
b1969_g1969



## - Births 1969 to Median HH Income 1969
b1969_medhh_1969 <- cor.test(regions$Births_1969, regions$Median_HH_Inc_1969, 
                    method = "pearson")
b1969_medhh_1969


## - Births 1969 to GDP Per Capita HH Income
b1969_percaphh1969 <- cor.test(regions$Births_1969, regions$Per_Capita_HH_Inc_1969, 
                    method = "pearson")
b1969_percaphh1969


########

## - Births 1979 to GDP 1979
b1979_g1979 <- cor.test(regions$Births_1979, regions$GDP_1979, 
                    method = "pearson")
b1979_g1979



## - Births 1969 to Median HH Income 1969
b1979_medhh_1979 <- cor.test(regions$Births_1979, regions$Median_HH_Inc_1979, 
                    method = "pearson")
b1979_medhh_1979


## - Births 1969 to GDP Per Capita HH Income
b1979_percaphh1979 <- cor.test(regions$Births_1979, regions$Per_Capita_HH_Inc_1979, 
                    method = "pearson")
b1979_percaphh1979

#######


## - Births 1979 to GDP 1979
b1989_g1989 <- cor.test(regions$Births_1989, regions$GDP_1989, 
                    method = "pearson")
b1989_g1989



## - Births 1989 to Median HH Income 1989
b1989_medhh_1989 <- cor.test(regions$Births_1989, regions$Median_HH_Inc_1989, 
                    method = "pearson")
b1989_medhh_1989


## - Births 1989 to GDP Per Capita HH Income
b1989_percaphh1989 <- cor.test(regions$Births_1989, regions$Per_Capita_HH_Inc_1989, 
                    method = "pearson")
b1989_percaphh1989

```

##
## -- From the graphs and correlation calculations--
### THERE IS POSITIVE CORRELTATION BETWEEN THE BIRTHS AND GDP, MEDIAN HOUSEHOLD INCOME AND PER CAPITA HOUSEHOLD INCOME