# CUNY    SPS    R-WORKSHOP
## Final Assignment
### Tage N Singh
#### This Project use A Consolidate Dataset From 1969 to 1989 and is accessed from github.
#### The Question ? ?
#### -- Is THERE CORRELATION ACROSS REGIONS/STATES (AND DC) IN THE US AMONG THE FOLLOWING : :
#### -- US BIRTH RATES
#### -- MEDIAN HOUSEHOLD INCOME
#### -- PER CAPITA HOUSEHOLD INCOME
#### -- US GROSS DEOMESTIC PRODUCT (GDP)
#### -- FOR THE DECADES ENDING 1969, 1979,1989
#### -- ( CURRENT DOLLARS)


### - (:

```{r,Introduction}
library(datasets)
library(ggplot2)
library(dplyr)




popstatsURL <- ("https://raw.githubusercontent.com/tagensingh/SPS-WRKSHP-R-FINAL-PROJECT/master/1-SPS-Project-Consolidate-Data.csv")
popstatsURL <- ("1-SPS-Project-Consolidate-Data.csv")
popstats1 <- read.table(file =popstatsURL, header = TRUE , sep = ",")

summary(popstats1)

```

#### -- Fixing The Headers

```{r, Headers}

popstats2 <- popstats1

names(popstats2)[1] <- "Region_Code"
names(popstats2)[2] <- "Region_Name"
names(popstats2)[3] <- "State_Code"
names(popstats2)[4] <- "State_Name"
names(popstats2)[5] <- "Births_1969"
names(popstats2)[6] <- "Births_1979"
names(popstats2)[7] <- "Births_1989"
names(popstats2)[8] <- "GDP_1969"
names(popstats2)[9] <- "GDP_1979"
names(popstats2)[10] <- "GDP_1989"
names(popstats2)[11] <- "Median_HH_Inc_1969"
names(popstats2)[12] <- "Median_HH_Inc_1979"
names(popstats2)[13] <- "Median_HH_Inc_19689"
names(popstats2)[14] <- "Per_Capita_HH_Inc_1969"
names(popstats2)[15] <- "Per_Capita_HH_Inc_1979"
names(popstats2)[16] <- "Per_Capita_HH_Inc_1989"

head(popstats2, 6)

```

####Computing the correlation By State

```{r,Computation_1}

popstats31 <- subset(popstats2, Region_code =="1",select=Region_Code:Per_Capita_HH_Inc_1989)
popstats32 <- subset(popstats2, Region_code =="2",select=Region_Code:Per_Capita_HH_Inc_1989)
popstats33 <- subset(popstats2, Region_code =="3",select=Region_Code:Per_Capita_HH_Inc_1989)
popstats34 <- subset(popstats2, Region_code =="4",select=Region_Code:Per_Capita_HH_Inc_1989)
popstats35 <- subset(popstats2, Region_code =="5",select=Region_Code:Per_Capita_HH_Inc_1989)
popstats36 <- subset(popstats2, Region_code =="6",select=Region_Code:Per_Capita_HH_Inc_1989)
popstats37 <- subset(popstats2, Region_code =="7",select=Region_Code:Per_Capita_HH_Inc_1989)
popstats38 <- subset(popstats2, Region_code =="8",select=Region_Code:Per_Capita_HH_Inc_1989)
popstats39 <- subset(popstats2, Region_code =="9",select=Region_Code:Per_Capita_HH_Inc_1989)
popstats310 <- subset(popstats2, Region_code =="10",select=Region_Code:Per_Capita_HH_Inc_1989)
popstats311<- subset(popstats2, Region_code =="11",select=Region_Code:Per_Capita_HH_Inc_1989)



head(popstats31, 6)
head(popstats32, 6)
head(popstats33, 6)
head(popstats34, 6)
head(popstats35, 6)
head(popstats36, 6)
head(popstats37, 6)
head(popstats38, 6)
head(popstats39, 6)
head(popstats310, 6)
head(popstats311, 6)


```
